Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2018-12-17 SI.tex
First change of manuscriot and figures

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
\usepackage{times}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{ltablex}
\usepackage{footnote}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

\usepackage{xr-hyper} 
%\usepackage{xr}
\externaldocument{paper}

@@

\newpage{}
%\section{Further Analysis of the 2D Polarizability Model}
%\label{sec:2D-pol}

%In this section, we discuss further topics about the 2D polarizability
%model proposed in the main text.

%\section{Profile of induced dipoles of 2D material}
%\label{sec:dipole-plot}
%Here we show in detail the
%$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
%the 2H-MoS$_{2}$ slab in main text Figure 1a. The
%density $\rho$ is calculated as the average value in the
%\textit{xy}-plane, and the value is shown in Figure
%\ref{fig:rho-profile}. As can be seen the induced charges on the
%MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
%SL size $L \gg$12 \AA{} as in the first principle calculations done in
%the main text, the induced dipoles from the periodic images do not
%interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.
%
%\begin{figure}[htbp]
%  \centering
%  \includegraphics[width=0.95\linewidth]{img/SI-dipole-MoS2.pdf}
%  \caption{Induced dipole profile of a 2H-MoS$_{2}$ slab inside the
%    superlattice, corresponding to main text Figure
%    \ref{main-fig-1}a. \textbf{a}. Scheme of the MoS$_{2}$ layer
%    inside the SL separated by vacuum layer. The dielectric constant
%    $\varepsilon_{\mathrm{SL}}$ is combined effect of the 2D
%    polarizability $\alpha_{\mathrm{2D}}$ and the vacuum
%    layer. \textbf{b}. $\Delta \rho$ as a function of $z$ around the
%    MoS$_{2}$ layer, green and red parts corresponding to negative and
%    positive induced charges. The external electric field
%    $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
%  \label{fig:rho-profile}
%\end{figure}

\section{Table of Contents}

@@

\section{Calculations using many-body Green function method and frequency-dependent quantities $\alpha_{\mathrm{2D}}(\omega)$ and $\varepsilon_{\mathrm{SL}}(\omega)$}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
  \caption{Variation of $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for monolayer BN 
calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.  
}
  \label{fig:GW-PBE-alpha}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-in_plane.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:GW-omega-in}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:GW-omega-out}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:GW-omega-in}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:GW-omega-out}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-in_plane.pdf}
  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
}
  \label{fig:BSE-omega-in}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-out_of_plane.pdf}
  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
}
  \label{fig:BSE-omega-out}
\end{figure}

>>>>

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
\usepackage{times}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{ltablex}
\usepackage{footnote}
\usepackage{braket}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

\usepackage{xr-hyper} 
%\usepackage{xr}
\externaldocument[main-]{paper}

@@

\newpage{}

\section*{Table of Contents}

@@

\section{Further analysis on the dielectric properties of 2D materials}

In this section we provide more analysis on the dielectric properties
of 2D materials, with focus on the dielectric properties calculated
using many-body Green function method (G$_0$W$_0$) and the
frequency-dependency of the superlattice dielectric functions and 2D
polarizabilities.

\subsection{Profile of induced dipoles of 2D material}
\label{sec:dipole-plot}
Here we show in detail the
$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
the 2H-MoS$_{2}$ slab in main text Figure 1a. The
density $\rho$ is calculated as the average value in the
\textit{xy}-plane, and the value is shown in Figure
\ref{fig:rho-profile}. As can be seen the induced charges on the
MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
SL size $L \gg$12 \AA{} as in the first principle calculations done in
the main text, the induced dipoles from the periodic images do not
interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.

\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.5\linewidth]{img/SI-dipole-MoS2.pdf}
 \caption{$\Delta \rho$ as a function of $z$ around the
   MoS$_{2}$ layer, corresponding to main text Figure
   \ref{main-fig-1}a. Green and red parts corresponding to negative and
   positive induced charges. The external electric field
   $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
 \label{fig:rho-profile}
\end{figure}

\subsection{Dielectric properties calculated using many-body Green function method and frequency dependency}
\label{ssec:gw}

Here we will show the results of dielectric properties calculated
using higher level of many-body Green function method (G$_0$W$_{0}$)
and with electron-hole interaction. We first compare the case of a
layer of hBN within an superlattice with varying size with the
dielectric properties calculated using PBE and G$_{0}$W$_{0}$ methods,
as shown in Figure
\ref{fig:GW-PBE-alpha}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ as functions of $L$, shown in
Figure \ref{fig:GW-PBE-alpha}a and \ref{fig:GW-PBE-alpha}b,
respectively, do not converge with $L$, while the corresponding 2D
polarizabilities in Figure \ref{fig:GW-PBE-alpha}c and
\ref{fig:GW-PBE-alpha}d are almost $L$-independent. It is worthnoting
that since the G$_{0}$W$_{0}$ method has better estimation of the bandgap, $\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller using G$_{0}$W$_{0}$ than PBE method.
\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
 \caption{Variation of dielectric properties and
   $\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for
   monolayer BN calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.
   \textbf{a}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ as function of
   $L$. \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$ as function of
   $L$ corresponding to
   \textbf{b}. \textbf{c}. $\varepsilon_{\mathrm{SL}}^{\perp}$ as
   function of $L$.  \textbf{d}. $\alpha_{\mathrm{2D}}^{\perp}$ as
   function of $L$. In all cases the values obtained using
   G$_{0}$W$_{0}$ method is smaller than that using PBE method due to
   better estimation of the bandgap.}
  \label{fig:GW-PBE-alpha}
\end{figure}

Next we will investigate the frequency-dependent dielectric properties of the 2D materials using various methods. The imaginary part of the frequency-dependent dielectric function of an periodic system is calculated using the following relation:

\begin{equation}
\begin{aligned}
  \label{eq:dft-dielectric}
\varepsilon_{\alpha\beta}^{(2)}(\omega)=\frac{4\pi e^2}{\Omega}\lim\limits_{q\rightarrow 0}\frac{1}{q^2}\sum_{v,c,\mathbf{k}}&2\omega_\mathbf{k}\delta(\epsilon_{c\mathbf{k}}-\epsilon_{v\mathbf{k}}-\omega) \\
&\times\braket{u_{c\mathbf{k}+q\mathbf{e}_\alpha}|u_{v\mathbf{k}}}\braket{u_{v\mathbf{k}}|u_{c\mathbf{k}+q\mathbf{e}_\beta}}
\end{aligned}
\end{equation}
Through the Kramers-Kronig transformation the real part of the dielectric function can be obtained as:

\begin{equation}
  \varepsilon_{\alpha\beta}^{(1)}(\omega)=1+\frac{2}{\pi}\int_0^\infty\frac{\varepsilon_{\alpha\beta}^{(2)}(\omega')\omega'}{\omega'^2-\omega^2}d\omega'
\end{equation}

We calculate the frequency-dependent dielectric properties of hBN with
varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$
with electron-hole interaction (G$_{0}$W$_{0}$+BSE). As shown in
Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out}, the
intensities of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
$\varepsilon_{\mathrm{SL}}^{\perp}(\omega)$ reduce with increasing $L$
throughout the whole frequency range. The $L$-dependency can also be
removed using Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-ref}, yielding lattice-independent
polarizabilities throughout the frequency domain.

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-in_plane.pdf}
 \caption{Dependence of in-plane dielectric properties on $L$ for
   monolayer BN calculated using PBE method: \textbf{a} Real part of
   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{b} Real part of
   $\alpha_{\mathrm{2D}}^{\parallel}$, \textbf{c} Imaginary part of
   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{d} Imaginary part of
   $\alpha_{\mathrm{2D}}^{\parallel}$.  The same {\bf k}-sampling is used
   in all simulations with the only variable quantity being $L$. }
  \label{fig:PBE-omega-in}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
   \caption{Dependence of out-of-plane dielectric properties on $L$ for
   monolayer BN calculated using PBE method: \textbf{a} Real part of
   $\varepsilon_{\mathrm{SL}}^{\perp}$, \textbf{b} Real part of
   $\alpha_{\mathrm{2D}}^{\perp}$, \textbf{c} Imaginary part of
   $\varepsilon_{\mathrm{SL}}^{\perp}$, \textbf{d} Imaginary part of
   $\alpha_{\mathrm{2D}}^{\perp}$.  The same {\bf k}-sampling is used
   in all simulations with the only variable quantity being $L$. }
  \label{fig:PBE-omega-out}
\end{figure}

We note that the result may change slightly when G$_{0}$W$_{0}$ method
is used. As shown in Figures \ref{fig:GW-omega-in} and
\ref{fig:GW-omega-out}, not only do the intensity of the dielectric
functions change with $L$, but also the peak positions. As a result
the obtained polarizabilities also show $L$-dependent peak shift. This
can be explained by the long-range nature of Coulomb interactions. In
fact the self-energy of the G$_{0}$W$_{0}$ system $\Sigma$, is determined by:
\begin{equation}
  \label{eq:GW-formula}
  \Sigma = i G_{0} W_{0} = i G_{0} \varepsilon^{-1} \nu
\end{equation}
where $G$ is the non-interacting Green function, and $\nu$ is the
Coulomb interaction. Since the dielectric constant $\varepsilon$
changes with $L$, the self energy as well quasi-particle energies of
the G$_{0}$W$_{0}$ method also varies with $L$. As a result we get
higher peak energy of the dielectric spectrum when $L$ increases. Such
peculiar $L$-dependency can be minimized when adding electron-hole
interaction through the Bethe-Salpethe equation (BSE), as shown in
Figures \ref{fig:BSE-omega-in} and \ref{fig:BSE-omega-out}. The
polarizabilities again becomes lattice-independent due to the
localization of excitons within the 2D material layer, which corrects the energy shift of G$_{0}$W$_{0}$ method.

Combining the accuray of bandgap estimation, reproducible results of
frequency-dependent dielectric properties and calculation efforts, the
choice of HSE06 hybrid functional seems used in the main text provides
best tradeoff between all aspects.

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
  \caption{Similar to Figure \ref{fig:PBE-omega-in} but calculated using G$_{0}$W$_{0}$ method. Peak shift can be observed in the dielectric function spectra.
}
  \label{fig:GW-omega-in}
\end{figure}

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
 \caption{Similar to Figure \ref{fig:PBE-omega-out} but calculated
   using G$_{0}$W$_{0}$ method. Peak shift can be observed in the
   dielectric function spectra.}
  \label{fig:GW-omega-out}
\end{figure}

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-in_plane.pdf}
  \caption{Similar as in Fig. \ref{fig:GW-omega-in} but taking into account electron-hole interactions at the level of 
  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
  The peak shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$.
}
  \label{fig:BSE-omega-in}
\end{figure}

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-out_of_plane.pdf}
  \caption{Similar as in Fig. \ref{fig:GW-omega-out} but taking into account electron-hole interactions at the level of 
  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
  The peak shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
}
  \label{fig:BSE-omega-out}
\end{figure}
